### 2014-09-10 paper/paper.Rmd
more code cleaning

```{r shortages, echo = FALSE, message = FALSE, warning = FALSE}
school2012.sub = school2012[, c("name", "SCHOOLID", "SC14Q02", "SC14Q07", "SC14Q10")]
student2012.sub = student2012[, c("name", "SCHOOLID", "PV1MATH", "PV1READ", "PV1SCIE")]

@@

df = scores_by_school %>% left_join(school2012.sub)
df$SC14Q02 <- factor(df$SC14Q02, labels=c(0,1,2,3))
df$SC14Q07 <- factor(df$SC14Q07, labels=c(0,1,2,3))
df$SC14Q10 <- factor(df$SC14Q10, labels=c(0,1,2,3))
df.mshort <- df[!is.na(df$SC14Q02),] %>% group_by(name, SC14Q02) %>% summarise(mmath2 = mean(mmath, na.rm=T))
#qplot(SC14Q02, mmath2, data = df.mshort, facets = ~name, 
#      xlab="Math teacher shortage (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
#      ylab="Math Score", geom=c("point","line"), group=name)
df.lshort <- df[!is.na(df$SC14Q10),] %>% group_by(name, SC14Q10) %>% summarise(mmath2 = mean(mmath, na.rm=T))
#qplot(SC14Q10, mmath2, data = df.lshort, facets = ~name, 
#      xlab="Library shortages (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
#      ylab="Math Score", geom=c("point","line"), group=name)
df2 <- summarise(group_by(df[!is.na(df$SC14Q02),], name, SC14Q02), teachers = mean(mmath, na.rm=T))
colnames(df2)[2] <- "levels"
df3 <- summarise(group_by(df[!is.na(df$SC14Q07),], name, SC14Q07), computers = mean(mmath, na.rm=T))
colnames(df3)[2] <- "levels"
df4 <- summarise(group_by(df[!is.na(df$SC14Q10),], name, SC14Q10), libmaterials = mean(mmath, na.rm=T))
colnames(df4)[2] <- "levels"
df.all <- merge(df2, df3)
df.all <- merge(df.all, df4)
df.m <- melt(df.all, id=c("name", "levels"))
colnames(df.m)[4] <- "math"
qplot(levels, math, data = df.m, facets = ~name, 
      xlab="Shortages (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
      ylab="Math Score", geom=c("point","line"), group=variable, colour=variable) +
      scale_colour_manual("Type", values=c("teachers"="#1B9E77", "computers"="#D95F02", "libmaterials"="#7570B3")) +
      theme(legend.position="bottom") 
#ggsave("shortages.pdf", width=14, height=14)
qplot(SC14Q02, data=df, geom="histogram", xlab="Teacher shortage", fill=I("#1B9E77"))
#ggsave("teacher-shortages.pdf", width=5, height=5)
qplot(SC14Q07, data=df, geom="histogram", xlab="Computer shortage", fill=I("#D95F02"))
#ggsave("computer-shortages.pdf", width=5, height=5)
qplot(SC14Q10, data=df, geom="histogram", xlab="Library materials shortage", fill=I("#7570B3"))
#ggsave("library-shortages.pdf", width=5, height=5)
```

@@

```{r studying, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
student.luke <- student2012[,c("CNT","PV1MATH","PV1READ","PV1SCIE","ST57Q01")]
study.luke <- melt(student.luke,id=c("CNT","ST57Q01"))
studyplot <- ggplot(data = study.luke, aes(ST57Q01,value,colour=variable) )+facet_wrap(~CNT)+stat_smooth(se=F)
studyplot
```

```{r studyingbar, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
studybar <- ggplot(data = study.luke, aes(ST57Q01) ) + geom_histogram(binwidth=4) + xlab("Hours spent studying")
studybar
```

>>>>

```{r shortages, fig.width=8, fig.height=12, warning=FALSE, message=FALSE, echo=FALSE}
school2012.sub = school2012[, c("name", "SCHOOLID", "SC14Q02", "SC14Q07", "SC14Q10")]
student2012.sub = student2012[, c("name", "SCHOOLID", "PV1MATH", "PV1READ", "PV1SCIE")]

@@

df = scores_by_school %>% left_join(school2012.sub)
df$SC14Q02 <- factor(df$SC14Q02, labels=c(0,1,2,3))
df$SC14Q07 <- factor(df$SC14Q07, labels=c(0,1,2,3))
df$SC14Q10 <- factor(df$SC14Q10, labels=c(0,1,2,3))
df.mshort <- df[!is.na(df$SC14Q02),] %>% group_by(name, SC14Q02) %>% summarise(mmath2 = mean(mmath, na.rm=T))
#qplot(SC14Q02, mmath2, data = df.mshort, facets = ~name, 
#      xlab="Math teacher shortage (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
#      ylab="Math Score", geom=c("point","line"), group=name)
df.lshort <- df[!is.na(df$SC14Q10),] %>% group_by(name, SC14Q10) %>% summarise(mmath2 = mean(mmath, na.rm=T))
#qplot(SC14Q10, mmath2, data = df.lshort, facets = ~name, 
#      xlab="Library shortages (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
#      ylab="Math Score", geom=c("point","line"), group=name)
df2 <- summarise(group_by(df[!is.na(df$SC14Q02),], name, SC14Q02), teachers = mean(mmath, na.rm=T))
colnames(df2)[2] <- "levels"
df3 <- summarise(group_by(df[!is.na(df$SC14Q07),], name, SC14Q07), computers = mean(mmath, na.rm=T))
colnames(df3)[2] <- "levels"
df4 <- summarise(group_by(df[!is.na(df$SC14Q10),], name, SC14Q10), libmaterials = mean(mmath, na.rm=T))
colnames(df4)[2] <- "levels"
df.all <- merge(df2, df3)
df.all <- merge(df.all, df4)
df.m <- melt(df.all, id=c("name", "levels"))
colnames(df.m)[4] <- "math"
qplot(levels, math, data = df.m, facets = ~name, 
      xlab="Shortages (0=None, 1=Very little, 2=To some extent, 3=A lot)", 
      ylab="Math Score", geom=c("point","line"), group=variable, colour=variable) +
      scale_colour_manual("Type", values=c("teachers"="#1B9E77", "computers"="#D95F02", "libmaterials"="#7570B3")) +
      theme(legend.position="bottom") 
#ggsave("shortages.pdf", width=14, height=14)
```

```{r shortagesbars, fig.width=4, fig.height=4, warning=FALSE, message=FALSE, echo=FALSE}
qplot(SC14Q02, data=df, geom="histogram", xlab="Teacher shortage", fill=I("#1B9E77"))
#ggsave("teacher-shortages.pdf", width=5, height=5)
qplot(SC14Q07, data=df, geom="histogram", xlab="Computer shortage", fill=I("#D95F02"))
#ggsave("computer-shortages.pdf", width=5, height=5)
qplot(SC14Q10, data=df, geom="histogram", xlab="Library materials shortage", fill=I("#7570B3"))
#ggsave("library-shortages.pdf", width=5, height=5)
```

@@

```{r studying, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
student.luke <- student2012[,c("name","PV1MATH","PV1READ","PV1SCIE","ST57Q01")]
study.luke <- melt(student.luke,id=c("name","ST57Q01"))
studyplot <- ggplot(data = study.luke, aes(ST57Q01, value, colour=variable)) + facet_wrap(~name) + stat_smooth(se=F)
studyplot
```

```{r studyingbar, fig.width=4, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
studybar <- ggplot(data = study.luke, aes(ST57Q01) ) + geom_histogram(binwidth=4) + xlab("Hours spent studying")
studybar
```
